---
title: 'Step 8 - Publishing Images'
teaching: 20
exercises: 1
---


The grand finale is approaching: Publication. How is it done?

::::::::::::::::::::::::::::::::::::::::::::::: instructor

Opportunity to ask people for ideas on what needs to be done, either on whiteboard or in chat.

::::::::::::::::::::::::::::::::::::::::::::::: 


::::::::::::::::::::::::::::::::::::::::::::::: discussion

### Resources

This publication - [Community-developed checklists for publishing images and image analyses](https://www.nature.com/articles/s41592-023-01987-9) - may be helpful.

:::::::::::::::::::::::::::::::::::::::::::::::


::::::::::::::::::::::::::::::::::::::::::::::: instructor

Does your institute have a 'Once your project is done' checklist?

May be worth checking with your library or research office.

::::::::::::::::::::::::::::::::::::::::::::::: 

```{r child="files/endOfProjChecklist.Rmd"}
```

# Where to deposit?

Deposit final state data to support your publications in an
institutional or discipline data repository which can mint a DOI and
create a citation for your work.

```{r child="files/dataDeposit.Rmd"}
```

[Here is a helpful guide to choosing a data repository](https://ardc.edu.au/resource/guide-to-choosing-a-data-repository/)

Some repositories include:

 - [Image Data Resource (IDR)] (https://idr.openmicroscopy.org/)

 - [BioImage Archive] (https://www.ebi.ac.uk/bioimage-archive/)

 - [Figshare](https://figshare.com/)

 - [Zenodo](https://zenodo.org/)

 - [Re3Data](https://www.re3data.org/)

 - [PLOSone Recommended Repositories](https://journals.plos.org/plosone/s/recommended-repositories)

Can you also publish your raw data?



### Publishing negative results

While it can be disheartening to get negative results, these results are still beneficial to the research community at large. 

You worked out something ***didn't work***, __which is important knowledge all in itself__. Sharing this means others don't need to reinvent the wheel, saving research effort and time.

There are a number of journals that specialise in these results.

[Positively Negative](https://everyone.plos.org/2015/02/25/positively-negative-new-plos-one-collection-focusing-negative-null-inconclusive-results/)

[The Missing Pieces](https://collections.plos.org/collection/missing-pieces/)

[Journal of Articles in Support of the Null Hypothesis](https://www.jasnh.com/)

[The All Results Journals](https://arjournals.com/)


::::::::::::::::::::::::::::::::::::::::::::::: discussion

### Information worth including in your paper or repository


 - Have limitations of the study been noted and justified/discussed?

 - Have you discussed how you handled missing data?

 - Should you include a reflective statement, with consideration on how your own bias/ priviledges/ world views may impact the findings?

::::::::::::::::::::::::::::::::::::::::::::::: 

::::::::::::::::::::::::::::::::::::::::::::::: challenge

## What if a collaborative relationship sours?

Imagine you have been working with a collaborative partner in a different organisation. As you finish your project, they state that they are no longer interested in working together and are going to apply for the next grant with another partner.

How will this affect you?

What steps have we taken so far to help protect our position?

:::::::::::::::::::::::::::::: solution

This may affect you 


However, we've already taken steps to protect ourselves and safeguard against any potential fallout.

We've documented our [ethics and governance](episodes/step4Doco.html) documents and have clarified the conditions around reuse of the data, whether the data can be shared and what the data can be used for.

We've licensed our pipelines and data to specify whether it can be reused or if it can be commercialised, and if we need to be cited.



:::::::::::::::::::::::::::::: 

::::::::::::::::::::::::::::::::::::::::::::::: 

::::::::::::::::::::::::::::::::::::::::::::::: discussion

### Useful Resources

[Ten simple rules for improving research data discovery](https://doi.org/10.1371/journal.pcbi.1009768)


[Ten simple rules for getting and giving credit for data](https://doi.org/10.1371/journal.pcbi.1010476)

[Citing Software by ARDC](https://ardc.edu.au/resource/citing-software/)


[Publishing a Jupyter notebook in a Findable, Accessible, Interoperable and Reusable (FAIR) way](https://ardc.edu.au/resource/fair-for-jupyter-notebooks-a-practical-guide/)


[Discontinuing a research software project?](https://bssw.io/blog_posts/discontinuing-a-research-software-project)

CESSDA Training Team (2017 - 2022). CESSDA Data Management Expert Guide. Bergen, Norway: CESSDA ERIC. Retrieved from https://dmeg.cessda.eu/Data-Management-Expert-Guide/6.-Archive-Publish licensed under a Creative Commons Attribution-ShareAlike 4.0 International License.

DOI Decision Tree for Data Managers Retrieved on 2024-04-17 at https://ardc.edu.au/resource/doi-decision-tree/ licenced as CC BY 4.0 as per https://au.creativecommons.net/attributing-cc-materials/


:::::::::::::::::::::::::::::::::::::::::::::::

# What is your next step?

::: tab 

### Beginner

A great place to start is:

Get yourself an ORCID id. This allows people to find and reach you easily. You can even include it in your email signature.


### Advanced

Your next move can be:

Prepare your data, analysis pipelines/protocols and materials for FAIR or open publication. Make sure you've got your IP and licence associated with your work.

:::



::::::::::::::::::::::::::::::::::::::::::::::: callout

## References

ARDC (2024) 'FAIR data'. Retrieved from https://ardc.edu.au/resource/fair-data/ licenced as CC-BY-4.0

[Project completion checklist](https://github.com/BahlaiLab/Policies/blob/master/Project_completion.md) by @cbahlai licenced under Public Domain


Contaxis N, Clark J, Dellureficio A, Gonzales S, Mannheimer S, Oxley PR, et al. (2022) Ten simple rules for improving research data discovery. PLoS Comput Biol 18(2): e1009768. https://doi.org/10.1371/journal.pcbi.1009768 licenced under CC-BY


ORCID (2024) Main Page. Retrieved on 2024-04-18 at https://orcid.org/ licenced as Public Domain.

Wood-Charlson EM, Crockett Z, Erdmann C, Arkin AP, Robinson CB (2022) Ten simple rules for getting and giving credit for data. PLoS Comput Biol 18(9): e1010476. https://doi.org/10.1371/journal.pcbi.1010476

Image:

 As per Sonja Bezjak, April Clyburne-Sherin, Philipp Conzett, Pedro Fernandes, Edit Görögh, Kerstin Helbig, Bianca Kramer, Ignasi Labastida, Kyle Niemeyer, Fotis Psomopoulos, Tony Ross-Hellauer, René Schneider, Jon Tennant, Ellen Verbakel, Helene Brinken, & Lambert Heller. (2018). Open Science Training Handbook (1.0)]. Zenodo. https://doi.org/10.5281/zenodo.1212496 , Retrieved 2024-04-19 from https://open-science-training-handbook.gitbook.io/book/02opensciencebasics/02openresearchdataandmaterials#undefined-3 licenced as CC0 Universal Public Domain.

:::::::::::::::::::::::::::::::::::::::::::::::

::::::::::::::::::::::::::::::::::::::::::::::: keypoints

### In this lesson, we have learnt:

- What the difference is between an identifier and a persistent identifier

- What a DOI and ORCID is

- How to get a DOI minted for your articles and datasets

- If and how to share your datasets

- What FAIR sharing is, and how mediated sharing works

- What to consider for licensing

- Where you can deposit your datasets or grey materials

- Negative results and how this still can be important to publish


#### We build trust in our knowledge by:

- Publishing our data with a license, so that others can reuse it

- Sharing your data as FAIR, so that people can find you and request your data in a safe way

- Helping people track who you are via an ORCID id


#### We retain knowledge using:

- Having our datasets saved with persistent URL links, so that they are never lost.

- Attaching our outputs and papers to our ORCID id, so that people can always find us as authors and our scope of work



#### We build business continuity by:

Attaching persistent identifiers to our data when publishing datasets, so that others in the team can reference them



:::::::::::::::::::::::::::::::::::::::::::::::
